---
title: ""
author: ""
date: ""
output: word_document
---

```{r setup, include=FALSE}
rm(list = ls())
library(tidyverse)
library(lme4)
library(lmerTest)
library(emmeans)


source("/Users/chelseawilmer/Desktop/Github/Phenology/Phenology.data.cleanup.R")

#make variables factors
pheno$Year <- as.factor(pheno$Year)
pheno$Site <- as.factor(pheno$Site)
pheno$PlotPair <- as.factor(pheno$PlotPair)
pheno$Plot_ID <- as.factor(pheno$Plot_ID)
pheno$Subplot_ID <- as.factor(pheno$Subplot_ID)
pheno$Treatment <- as.factor(pheno$Treatment)
pheno$Species <- as.factor(pheno$Species)
pheno$Functional.Type <- as.factor(pheno$Functional.Type)
pheno$Elevation <- as.integer(pheno$Elevation)

year <- filter(pheno, Treatment == "Control")
treatment <- filter(pheno, Year == 2018)
treatment <- filter(treatment, Site == "LM" | Site == "UM" | Site == "LSA" | Site == "USA")

```

###### 1. NL ~ Site*Year + Species + (1|PlotPair) + (1|Plot_ID) + (1|Subplot_ID), data = year)
```{r, echo=FALSE}
model1 <- lmer(NL ~ Site*Year + Species + (1|PlotPair) + (1|Plot_ID) + (1|Subplot_ID), data = year)
anova(model1, ddf = "Kenward-Roger")

emmeans(model1, pairwise ~ Year|Site)

```

###### 2. FLE ~ Site*Year + Species + (1|PlotPair) + (1|Plot_ID) + (1|Subplot_ID), data = year)
```{r, echo=FALSE}
model2 <- lmer(FLE ~ Site*Year + Species + (1|PlotPair) + (1|Plot_ID) + (1|Subplot_ID), data = year)

anova(model2, ddf = "Kenward-Roger")

emmeans(model2, pairwise ~ Year|Site)
```

###### 3. FOF ~ Site*Year + Species + (1|PlotPair) + (1|Plot_ID) + (1|Subplot_ID), data = year)
```{r, echo=FALSE}

```

###### 4. FLCC ~ Site*Year + Species + (1|PlotPair) + (1|Plot_ID) + (1|Subplot_ID), data = year)
```{r, echo=FALSE}

```

###### 5. NL ~ Site*Treatmemt + Species + (1|PlotPair) + (1|Plot_ID) + (1|Subplot_ID), data = treatment)
```{r, echo=FALSE}
model5 <- lmer(NL ~ Site*Treatment + Species + (1|PlotPair) + (1|Plot_ID) + (1|Subplot_ID), data = treatment)
anova(model5, ddf = "Kenward-Roger")

emmeans(model5, pairwise ~ Treatment|Site)
```

###### 6. FLE ~ Site*Treatment + Species + (1|PlotPair) + (1|Plot_ID) + (1|Subplot_ID), data = treatment)
```{r, echo=FALSE}
model6 <- lmer(FLE ~ Site*Treatment + Species + (1|PlotPair) + (1|Plot_ID) + (1|Subplot_ID), data = treatment)
anova(model6, ddf = "Kenward-Roger")

emmeans(model6, pairwise ~ Treatment|Site)

```

###### 7. FOF ~ Site*Treatmemt + Species + (1|PlotPair) + (1|Plot_ID) + (1|Subplot_ID), data = treatment)
```{r, echo=FALSE}

```

###### 8. FLCC ~ Site*Treatmemt + Species + (1|PlotPair) + (1|Plot_ID) + (1|Subplot_ID), data = treatment)
```{r, echo=FALSE}

```

###### 9. 
```{r, echo=FALSE}

```

###### 10. 
```{r, echo=FALSE}

```

###### 11. 
```{r, echo=FALSE}

```